### 2020-12-19 ch/1-introduction.tex
Write almost nothing

>>>>

The final approach is in the setting of sampling bias as well,
but compared to the previous method, we relax some assumptions and get other trade-offs.
The main motivation is to not require access to $s$ labels in the context set,
such that in the setting, we have a completely unlabeled context set
and a training set which is missing certain combinations of $s$ and $y$.
In this setting, it is possible to learn an invariant representation
by enforcing the representation for the training set to be indistinguishable from the representation on the context set,
when conditioning on $y$.
